From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-06-02 paper.tex
Minor Livre tweak
Abstract

\begin{abstract}
  The Blue Brain project has been investing in high-performance visualization
  (HPV) to complement its HPC strategy since its inception in 2007. In 2011,
  this strategy has been accelerated to develop innovative visualization
  solutions through through increased funding and strategic partnerships with
  other research institutions.

  We present the key elements of this HPV ecosystem, which integrates C++
  visualization applications with novel collaborative display systems. We
  motivate how our strategy of transforming high-performance visualization
  engines into services enables a variety of use cases, not only for the
  integration with high-fidelity displays, but also to build service oriented
  architectures, to link into web applications and to provide remote services to
  python applications.
\end{abstract}

@@

Visualization supports the BBP along all parts of this project to understand and
debug model data, building and simulation algorithms as well as validating and
discovering new insight from the in-silico experiments. Our strategy to support
this mission is based on components linked through network protocols:
High-fidelity display systems to see more detail in complex data, a set of
standard rendering engines (rasterization, out-of-core volume rendering,
interactive raytracing), and decoupled, light-weight applications using remote
these components. In the following we will present these components along with a
few use cases.

@@

In our out-of-core data access layer, multi-resolution data is represented as an
octree data structure. This representation accelerates the selection of the
proper level-of-detail and to track the status of the LODs (in CPU memory, in
GPU memory, not loaded). While rendering, view-based LOD selection is performed
using the screen-space-error (SSE)~\cite{guthe2004} technique. \fig{fLivre}
shows the rendering of 300 GB volume with an illustration of the selected LOD
levels.

\begin{figure}[h!t]
    \includegraphics[width=.45\columnwidth]{images/livre}\hfill
    \includegraphics[width=.45\columnwidth]{images/livreLOD}
  \caption{\label{fLivre}Livre rendering a 300GB vasculature dataset (left) and
    the selected LODs (right)}
\end{figure}

@@

\begin{wrapfigure}{r}{.382\textwidth}\center\vspace{-6ex}
  \includegraphics[width=.382\textwidth]{images/ZeroMS}
  {\caption{\label{fZero}Messaging enables new use cases}}\vspace{-2ex}
\end{wrapfigure}

>>>>

\begin{abstract}
  Blue Brain has pushed high-performance visualization (HPV) to complement its
  HPC strategy since its inception in 2007. In 2011, this strategy has been
  accelerated to develop innovative visualization solutions through increased
  funding and strategic partnerships with other research institutions.

  We present the key elements of this HPV ecosystem, which integrates C++
  visualization applications with novel collaborative display systems. We
  motivate how our strategy of transforming visualization engines into services
  enables a variety of use cases, not only for the integration with
  high-fidelity displays, but also to build service oriented architectures, to
  link into web applications and to provide remote services to python
  applications.
\end{abstract}

@@

Visualization supports the BBP along all parts of the project to understand and
debug model data, building and simulation algorithms as well as validating and
discovering new insight from the in-silico experiments. Our strategy to support
this mission is based on components linked through network protocols:
High-fidelity display systems to see more detail in complex data, a set of
standard rendering engines (rasterization, out-of-core volume rendering,
interactive raytracing), and decoupled, light-weight applications using remote
these components. In the following we will present these components along with a
few use cases.

@@

In our out-of-core data access layer, multi-resolution data is represented as an
octree data structure. This representation accelerates the selection of the
proper level-of-detail and to track the status of the LODs (in CPU memory, in
GPU memory, not loaded). While rendering, view-based LOD selection is performed
using the screen-space-error (SSE)~\cite{guthe2004} technique. \fig{fLivre}
shows the rendering of a MicroCT dataset with an illustration of the selected
LOD levels.

\begin{figure}[h!t]
    \includegraphics[width=.45\columnwidth]{images/livre}\hfill
    \includegraphics[width=.45\columnwidth]{images/livreLOD}
  \caption{\label{fLivre}Livre rendering a MicroCT dataset (left) and
    the selected LODs (right)}
\end{figure}

@@

\begin{wrapfigure}{r}{.382\textwidth}\center\vspace{-6ex}
  \includegraphics[width=.382\textwidth]{images/ZeroMS}
  {\caption{\label{fZero}New messaging use cases}}\vspace{-2ex}
\end{wrapfigure}
